\documentclass{article}
\usepackage{graphicx}
\usepackage{caption}
\graphicspath{ {./images/} }
 
\begin{document}
\paragraph{A Look at the Captured Trace}
  \begin{enumerate}
    \item Select the first ICMP echo request message sent by your computer and expand the internet protocol part of the packet int he packet detials window.  What ist he IP address of your computer?
            \begin{itemize}
            \item A
          \end{itemize}

      \item Within the IP packet header, what is the value in the upper layer protocol field?
          \begin{itemize}
            \item A
          \end{itemize}

      \item How many bytes are in the ip header?  How many bytes are in the payload of the IP datagram?  Explain how you determined the number of payload bytes.
          \begin{itemize}
            \item A
          \end{itemize}

      \item Has this IP datagram been fragmented?  Explain how you determined whether or not the datagram has been fragmented?
          \begin{itemize}
            \item A
          \end{itemize}

      \item Which fields in the IP datagram always change from one datagram to the next within this series of ICMP messages sent by your computer?
          \begin{itemize}
            \item A
          \end{itemize}

      \item Which field stays constatn?  Which of the fields must stay constant?  Which fields must change? Why?
          \begin{itemize}
            \item A
          \end{itemize}

      \item Describe the pattern you see in the values in the IDentification field of the IP Datagram 
          \begin{itemize}
            \item A
          \end{itemize}


      \item What is the value in the Identification field and the TTL field? 
          \begin{itemize}
            \item A
          \end{itemize}

      \item Do these values remain uncahnged for all of the ICMP TTL-exceeded replies sent to your computer by the nearest (first hop) router? Why? 
          \begin{itemize}
            \item A
          \end{itemize}

      \paragraph{Fragmentation}
      \item Find the first ICMP echo request message that was sent by your computer after you changed the Packet Size in pingplotter to be 200.
          \begin{itemize}
            \item A
          \end{itemize}

      \item Print out the first fragment of the fragmented IP datagram.  What information in the IP header indicates that the datagram has been fragmented?  What information in the IP header indicates whether thsi is the first fragment
      versus a latter frament?  How long is this IP Datagram?
          \begin{itemize}
            \item A

    \end{itemize}
  \end{enumerate}
\end{document}
